---
title: "AHSize"
author: "Emanuele Giacomuzzo"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
output: 
  html_document:
     code_folding: hide
html_document:
    toc: true
    toc_float: true
    code_folding: hide
    number_sections: true
    includes:
      after_body: tabset-dropdown.html
editor_options: 
  chunk_output_type: console
---

#  {.tabset}

## Design

```{r child = here::here("r_markdown_files", "01_show_design.Rmd"), echo=FALSE}
```

## Parameters {.tabset .tabset-dropdown}

```{r child = here::here("r_markdown_files", "02_set_packages.Rmd"), echo = FALSE, message = FALSE, cache = FALSE, autodep = FALSE}
```

```{r child = here("r_markdown_files", "03_set_functions.Rmd")}
```

```{r child = here("r_markdown_files", "04_set_parameters.Rmd"), class.source = 'fold-show'}
```

## Data {.tabset .tabset-dropdown}

### Produce data from videos

```{r child = here("r_markdown_files", "05_generate_data_from_videos.Rmd"), class.source = 'fold-show', eval = FALSE}
```

### Individuals (`ds_individuals`)

```{r child = here("r_markdown_files", "06_create_ds_individuals_assemble.Rmd"), class.source = 'fold-show'}
```

```{r child = here("r_markdown_files", "07_create_ds_individuals_species_ID.Rmd"), class.source = 'fold-show'}
```

### Ecosystems (`ds_ecosystems`)

```{r child = here("r_markdown_files", "08_create_ds_ecosystems.Rmd"), class.source = 'fold-show'}
```

### Species dominances with CI (`ds_dominances_with_CI`)

```{r child = here("r_markdown_files", "09_create_ds_dominances_with_CI.Rmd"), class.source = 'fold-show'}
```

### Ecosystems effect sizes (`ds_ecosystems_effect_size`)

```{r child = here("r_markdown_files", "10_create_ds_ecos_effect_size.Rmd"), class.source = 'fold-show'}
```

### Species effect sizes d (`ds_species_effect_sizes_d`)

```{r child = here("r_markdown_files", "11_create_ds_species_effect_sizes_d.Rmd"), class.source = 'fold-show'}
```

### Species effect sizes LRR (`ds_species_effect_sizes_LRR`)

```{r child = here("r_markdown_files", "12_create_ds_species_effect_sizes_LRR.Rmd"), class.source = 'fold-show'}
```

### Meta-ecosystems (`ds_metaecosystems`)

```{r child = here("r_markdown_files", "13_create_ds_metaecosystems.Rmd"), class.source = 'fold-show'}
```

### Unconnected combination sets (`unconnected_combinations_sets` & `sets_of_sets`)

```{r child = here("r_markdown_files", "14_create_unconnected_combinations_sets.Rmd"), class.source = 'fold-show'}
```

```{r child = here("r_markdown_files", "15_create_ds_classes.Rmd"), eval = FALSE}
```

## Plots & analysis {.tabset .tabset-dropdown}

### Meta-ecosystems {.tabset .tabset-pills}

```{r child = here("r_markdown_files", "16_analyse_metaecos.Rmd")}
```

### Autotrophic ecosystems {.tabset .tabset-pills}

```{r}
trophy_selected = "autotrophic"
```

#### Biomass {.tabset .tabset-dropdown}

```{r}
response_variable_selected = "bioarea_mm2_per_ml"
distribution_selected = "tweedie"
```

```{r child = here("r_markdown_files", "17_analyse_ecos.Rmd")}
```

#### Median body size {.tabset .tabset-dropdown}

```{r}
response_variable_selected = "median_body_size_µm2"
distribution_selected = "tweedie"
```

```{r child = here("r_markdown_files", "17_analyse_ecos.Rmd")}
```

```{r results=FALSE}

# --- SAVE PLOT --- #

# Generate the image where to save the plot

pdf(file = here("..",
                "3_results", 
                "figures", 
                "paper", 
                "ecosystems_median_body_size_auto.pdf"),
    width = paper_width_inches,
    height = paper_height_inches)

# Save image to the file

plot

# Close the current graphics device to properly save the image

dev.off()
```

### Heterotrophic ecosystems {.tabset .tabset-pills}

```{r}
ecosystem_type_i = c("Small heterotrophic unconnected",
                     "Medium heterotrophic unconnected",
                     "Large heterotrophic unconnected",
                     "Small heterotrophic connected",
                     "Medium heterotrophic connected",
                     "Large heterotrophic connected")

ecosystem_size_and_trophy_selected = c("Small heterotrophic",
                                       "Medium heterotrophic",
                                       "Large heterotrophic")

trophy_selected = "heterotrophic"
```

#### Biomass {.tabset .tabset-dropdown}

```{r}
response_variable_selected = "bioarea_mm2_per_ml"
distribution_selected = "tweedie"
```

```{r child = here("r_markdown_files", "17_analyse_ecos.Rmd")}
```

#### Species richness {.tabset .tabset-dropdown}

```{r}
response_variable_selected = "species_richness"
distribution_selected = "gaussian"
```

```{r child = here("r_markdown_files", "17_analyse_ecos.Rmd")}
```

#### Shannon {.tabset .tabset-dropdown}

```{r}
response_variable_selected = "shannon"
distribution_selected = "gaussian"
```

```{r child = here("r_markdown_files", "17_analyse_ecos.Rmd")}
```

```{r results=FALSE}

# --- SAVE PLOT --- #

# Generate the image where to save the plot

pdf(file = here("..",
                "3_results", 
                "figures", 
                "paper", 
                "ecosystems_shannon_hetero.pdf"),
    width = paper_width_inches,
    height = paper_height_inches)

# Save image to the file

plot

# Close the current graphics device to properly save the image

dev.off()
```

#### Evenness {.tabset .tabset-dropdown}

```{r}
response_variable_selected = "evenness_pielou"
distribution_selected = "gaussian"
```

```{r child = here("r_markdown_files", "17_analyse_ecos.Rmd")}
```

#### Median body size {.tabset .tabset-dropdown}

```{r}
response_variable_selected = "median_body_size_µm2"
distribution_selected = "tweedie"
```

```{r child = here("r_markdown_files", "17_analyse_ecos.Rmd")}
```

```{r results=FALSE}

# --- SAVE PLOT --- #

# Generate the image where to save the plot

pdf(file = here("..",
                "3_results", 
                "figures", 
                "paper", 
                "ecosystems_median_body_size_hetero.pdf"),
    width = paper_width_inches,
    height = paper_height_inches)

# Save image to the file

plot

# Close the current graphics device to properly save the image

dev.off()
```

#### Total individuals {.tabset .tabset-dropdown}

```{r}
response_variable_selected = "indiv_per_ml"
distribution_selected = "tweedie"
```

```{r child = here("r_markdown_files", "17_analyse_ecos.Rmd")}
```

#### Dominance {.tabset .tabset-dropdown}

##### Hedge's {.tabset}

```{r child = here("r_markdown_files", "18_analyse_ecos_dominance_d.Rmd")}
```

##### Log Response Ratio {.tabset}

```{r child = here("r_markdown_files", "19_analyse_ecos_dominance_LRR.Rmd")}
```

#### BEF

```{r child = here("r_markdown_files", "20_analyse_ecos_BEF.Rmd")}
```

## Figures

```{r child = here("r_markdown_files", "21_set_parameters_results.Rmd")}
```

```{r child = here("r_markdown_files", "22_save_plot_paper_metaecos.Rmd")}
```

```{r child = here("r_markdown_files", "23_save_plot_paper_ecos_biomass.Rmd")}
```

<details>
<summary>Presentation meta-ecosystems</summary>
```{r child = here("r_markdown_files", "24_save_plot_presentation_metaecos.Rmd")}
```
</details>

<details>
<summary>Presentation plots autotrophic-dominated ecosystems</summary>
```{r}
metaecosystem_type_selected = "autotrophic-dominated"
```

```{r child = here("r_markdown_files", "25_save_plot_presentation_ecos_biomass.Rmd")}
```
</details>

<details>
<summary>Presentation plots heterotrophic-dominated ecosystems</summary>
```{r}
metaecosystem_type_selected = "heterotrophic-dominated"
```

```{r child = here("r_markdown_files", "25_save_plot_presentation_ecos_biomass.Rmd")}
```
</details>

## Other {.tabset .tabset-dropdown}

```{r child = here("r_markdown_files", "26_show_other.Rmd")}
```