---
title: "Untitled"
output: html_document
date: "2023-12-18"
editor_options: 
  chunk_output_type: console
---

In the previous section of code, we identified combinations of ecosystems that form unconnected meta-ecosystems. However, directly comparing all unconnected meta-ecosystems to connected ones would inflate our degrees of freedom due to autocorrelation among unconnected meta-ecosystems sharing the same ecosystem. To address this, we will compare five connected meta-ecosystems to five unconnected meta-ecosystems in the analysis, each comparison comprising different combinations of unconnected meta-ecosystems. In each comparison, we create a "combination set" of unconnected meta-ecosystems. For each combination set (e.g., equally-dominated unconnected), we assign numerical order to the first ecosystem type (e.g., medium heterotrophic) and permute the order of the second type's ecosystems (e.g., medium autotrophic). For example, let's sat we are trying to create combination sets of equally-dominated unconnected where the first ecosystem type is medium heterotrophic (1,2,3,4,5), and the second type is medium autotrophic (6,7,8,9,10). Combinations of the first ecosystem type in numerical order (1,2,3,4,5; 1,2,3,4,5; etc.) and permutations of the second ecosystem type  (e.g., 6,7,8,9,10; 6,7,8,10,9; etc.) would give us the following: 1\|6, 1\|7, 1\|8, 1\|9, 1\|10; 1\|6, 1\|7, 1\|8, 1\|10, 1\|9; etc. To create an object which combines heterotrophic-dominated, equally-dominated, and autotrophic-dominated unconnected meta-ecosystem sets (`sets_of_sets`) we need to go through the following steps. (1) Create a function to combine unconnected meta-ecosystems into sets where each ecosystem appears only once. (2) Find the combination sets for heterotrophic-dominated, equally-dominated, and autotrophic-dominated unconnected meta-ecosystems. (3) Find the sets of sets in which you combine all three heterotrophic-dominated, equally-dominated, and autotrophic-dominated unconnected meta-ecosystems (`sets_of_sets`).

```{r}

# --- CREATE FUNCTION TO COMBINE UNCONNECTED META-ECOSYSTEMS --- #

create.unconnected.sets = function(metaeco_type_n_connection_selected,
                                   ecosystem_type_1,
                                   ecosystem_type_2) {
  
  # Find ID of the two ecosystems 
  
  ID_ecosystem_type_1 = ds_ecosystems %>%
    filter(ecosystem_type == ecosystem_type_1) %>%
    pull(ecosystem_ID) %>%
    unique()
  
  ID_ecosystem_type_2 = ds_ecosystems %>%
    filter(ecosystem_type == ecosystem_type_2) %>%
    pull(ecosystem_ID) %>%
    unique()
  
  # Create dataset with sets of unconnected meta-ecosystems
  
  two_ecosystem_unconnected_sets <- data.frame(
    
    # Give information on meta-ecosystem 
    
    metaeco_type = gsub(" unconnected", "", metaeco_type_n_connection_selected),
    connection = "unconnected",
    metaeco_type_n_connection = metaeco_type_n_connection_selected,
    
    # Repeat the IDs of the ecosystem type 1 for as many times as the 
    # permutations of ecosystem type 2
    
    ID_first_ecosystem = rep(ID_ecosystem_type_1, 
                             times = length(permn(ID_ecosystem_type_2))),
    
    # Permute the IDs of the ecosystem type 2
    
    ID_second_ecosystem = unlist(flatten(permn(ID_ecosystem_type_2))),
    
    # To have each set of unconnected meta-ecosystems to have a number, repeat 
    # the IDs of the ecosystem type ... for the number of ecosystem IDs of the 
    # ecosystem type ... (WARNING: if you want to do this code for another 
    # dataset it has to be done differently if you are taking off some 
    # ecosystems).
    
    set = rep(1 : length(permn(ID_ecosystem_type_2)), 
              each = length(ID_ecosystem_type_1))) %>%
    
    # To don't have problematic ecosystems, take them off (in our ecosystems 
    # we don't have to take them off though). 
    
    filter(!ID_first_ecosystem %in% ecosystems_to_take_off,
           !ID_second_ecosystem %in% ecosystems_to_take_off) %>%
    
    # To include other information for each unconnected metaecosystem, join 
    # with ecosystem_combinations.
    
    full_join(ecosystem_combinations %>%
              filter(metaeco_type_n_connection == 
                     metaeco_type_n_connection_selected)) %>%
    select(set,
           system_nr,
           metaeco_type,
           connection,
           metaeco_type_n_connection,
           ID_first_ecosystem,
           ID_second_ecosystem,
           ecosystems_combined)
  
  # Return object 'two_ecosystem_unconnected_sets'
  
  return(two_ecosystem_unconnected_sets)
  
}
```

```{r}

## - (2) Find the combination sets for heterotrophic-dominated, equally-dominated, and autotrophic-dominated unconnected meta-ecosystems. - ##

unconnected_combinations_sets = rbind(
  create.unconnected.sets("autotrophic-dominated unconnected",
                          "small heterotrophic unconnected",
                          "large autotrophic unconnected"),
  create.unconnected.sets("heterotrophic-dominated unconnected",
                          "large heterotrophic unconnected",
                          "small autotrophic unconnected"),
  create.unconnected.sets("equally-dominated unconnected",
                          "medium heterotrophic unconnected",
                          "medium autotrophic unconnected"))
```

```{r}

## - (3) Find the sets of sets in which you combine all three heterotrophic-dominated, equally-dominated, and autotrophic-dominated unconnected meta-ecosystems (sets_of_sets). - ##

sets_of_sets = expand.grid(autotrophic_dominated_set_n = unconnected_combinations_sets %>%
                             filter(metaeco_type_n_connection == "autotrophic-dominated unconnected") %>%
                             pull(set) %>%
                             unique(),
                           heterotrophic_dominated_set_n = unconnected_combinations_sets %>%
                             filter(metaeco_type_n_connection == "heterotrophic-dominated unconnected") %>%
                             pull(set) %>%
                             unique(),
                           equally_dominated_set_n = unconnected_combinations_sets %>%
                             filter(metaeco_type_n_connection == "equally-dominated unconnected") %>%
                             pull(set) %>%
                             unique())
```
