---
title: "Untitled"
output: html_document
date: "2023-11-28"
editor_options: 
  chunk_output_type: console
---

###### Small ecosystems

```{r class.source = 'fold-show'}
print_dominance("small heterotrophic unconnected")
print_dominance("small heterotrophic connected")
```

```{r warning=FALSE}
for(time_point_i in 2:4){
    
    print(paste("Time point ", time_point_i))
    
    p = ds_species_effect_sizes_d %>%
      filter(ecosystem_type == "small heterotrophic connected",
             time_point == time_point_i,
             species != "Eug") %>%
      ggplot(aes(x = species,
                 y = effect_size)) + 
      geom_pointrange(aes(ymin = lower_95_CI, ymax = upper_95_CI)) + 
      geom_hline(yintercept = 0, linetype = "dotted") +
      theme_bw() +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position = legend_position,
            legend.key.width = unit(legend_width_cm, "cm"))
    
    print(p)
    
  }
```


###### Medium ecosystems

```{r class.source = 'fold-show'}
print_dominance("medium heterotrophic unconnected")
print_dominance("medium heterotrophic connected")
```

```{r warning=FALSE}
for(time_point_i in 2:4){
    
    print(paste("Time point ", time_point_i))
    
    p = ds_species_effect_sizes_d %>%
      filter(ecosystem_type == "medium heterotrophic connected",
             time_point == time_point_i,
             species != "Eug") %>%
      ggplot(aes(x = species,
                 y = effect_size)) + 
      geom_pointrange(aes(ymin = lower_95_CI, ymax = upper_95_CI)) + 
      geom_hline(yintercept = 0, linetype = "dotted") +
      theme_bw() +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position = legend_position,
            legend.key.width = unit(legend_width_cm, "cm"))
    
    print(p)
    
  }
```

###### Large ecosystems

```{r class.source = 'fold-show'}
print_dominance("large heterotrophic unconnected")
print_dominance("large heterotrophic connected")
```

```{r warning=FALSE}
for(time_point_i in 2:4){
    
    print(paste("Time point ", time_point_i))
    
    p = ds_species_effect_sizes_d %>%
      filter(ecosystem_type == "large heterotrophic connected",
             time_point == time_point_i,
             species != "Eug") %>%
      ggplot(aes(x = species,
                 y = effect_size)) + 
      geom_pointrange(aes(ymin = lower_95_CI, ymax = upper_95_CI)) + 
      geom_hline(yintercept = 0, linetype = "dotted") +
      theme_bw() +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position = legend_position,
            legend.key.width = unit(legend_width_cm, "cm"))
    
    print(p)
    
  }
```

###### Together

The connection affected community composition in small, medium, and large heterotrophic patches. In small heterotrophic patches, the connection increased the dominance of Pau (t3) and decreased the one of Col (t3-4) and Pca (t4). In the medium heterotrophic patches, the connection increased the dominance of Ble (t2-3) and Pau (t4). In the large heterotrophic patches, the connection increased the dominance of Ble (t2) and Col (t2).