---
title: "Untitled"
output: html_document
date: "2023-11-16"
editor_options: 
  chunk_output_type: console
---

Figure 2. The effect of the autotrophic-heterotrophic spatial feedback on meta-ecosystem biomass was tuned by patch size. The effects of the spatial feedback on total meta-ecosystem biomass were positive in Autotrophic Dominated meta-ecosystems (they had higher total bioarea than Autotrophic Dominated isolated), negative in Heterotrophic Dominated meta-ecosystems (they had lower total bioarea than Heterotrophic Dominated isolated), and non-significant in Equally Dominated meta-ecosystems (they had the same total bioarea than Equally Dominated isolated). Heterotrophic-dominated meta-ecosystems: meta-ecosystems with one big heterotrophic and one small autotrophic patch. Autotrophic-dominated meta-ecosystems: meta-ecosystems with one big autotrophic and one small heterotrophic patch. Heterotrophic-dominated isolated: systems composed of one big heterotrophic and one small autotrophic isolated patch. Autotrophic-dominated isolated: systems with one big autotrophic and one small heterotrophic isolated patch.

```{r results = FALSE}

# --- CREATE THE META-ECOSYSTEM PLOT FOR THE PAPER --- #

# Generate the image where to save the plot

pdf(file = here("..", 
                "3_results", 
                "figures", 
                "paper", 
                "metaecosystems_1.pdf"),
    width = paper_width_inches,
    height = paper_height_inches) 

# Create plot

p = plot.metaecos.points(data = ds_metaecosystems,
                         response_variable = "total_metaecosystem_bioarea_mm2")

# Modify the plot to be saved using ggarrange

ggpubr::ggarrange(p +
                    theme(plot.margin = unit(c(ggarrange_margin_left,
                                               ggarrange_margin_right,
                                               ggarrange_margin_bottom,
                                               ggarrange_margin_left),
                                             "cm")) +
                    scale_x_continuous(breaks = unique(ds_ecosystems$day)),
                  align = "v",
                  label.x = 0.1,
                  label.y = 0.8)

# Close the current graphics device to properly save the image

dev.off()
```

```{r fig.height = figures_height_rmd_output}

# --- SHOW THE META-ECOSYSTEM PLOT FOR THE PAPER --- #

p
```