---
title: "AHSizePilot: data_manipulation_ecosystems_averaged"
output: html_document
date: "2022-11-15"
editor_options: 
  chunk_output_type: console
---

To analyse how strong the effects of the connection on the biomass, biodiversity, and population densities within ecosystems were, we want to compile a dataset (`ds_ecosystems_effect_size`) where each row represents the effect size of a connected vs unconnected ecosystem type (e.g., small autotrophic connected vs unconnected) at a time point. If the 95% CI of the effect size crosses the zero line it means that it is statistically significant. We use the effect size Hedge's d (aka Hedge's g), as it can handle the treatment and/or control equal to zero (log response ratio cannot: ln(treatment/0) = Inf; ln(0/control) = -inf; ln(0/0) = Nan), small sample sizes ("*it works well when there are as few as five to ten studies",* @Rosenberg2013), and unequal variance between treatment and control ([@Rosenberg2013]). Hedge's d (d) is the difference in mean between treatment and control divided by by their weighted spread (denominator) multiplied by a factor (J) that controls for small sample sizes [@Rosenberg2013]. The 95% confidence interval of Hedge's d is calculated from its standard error (SE) as [@Hedges1985] $d ± 1.96 * SE$ where the standard error is calculated as show in @Borenstein2009.

We calculate Hedge's d and its 95 % confidence interval in three steps. (1) Calculate means, standard deviations and sample sizes. Calculate the mean of the treatment (Y1) and control (Y2), the standard deviation of the treatment (s1) and the control (s2), as well as the sample size of the treatment (n1) and the control (n2) at each time point and for each response variable. (2) Calculate Hedge's d. Use means, standard deviations and sample sizes to calculate effect sizes. (3) Retain only the treatments (connected ecosystems), discarding the controls (unconnected). This is because we calculated the effect size of only connected compared to unconnected and not the other way around.

$$
d = \frac{Y1 - Y2}{denominator} * J
$$

$$
denominator = \sqrt{\frac{(n_1-1)*s_1^2 + (n_2 - 1) * s_2^2}{n_1 + n_2 - 2}}
$$

$$
J = 1 - \frac{3}{(4 * (n_1 + n_2 - 2)) - 1}
$$

$$
SE = \sqrt{J^2 * \frac{n_1 + n_2}{n_1*n_2} + \frac{d^2}{2*(n_1 + n_2)}}
$$

<br>

```{r}

## - (1) Calculate means, standard deviations and sample sizes. - ##

for (variable in 1:length(variables_ecosystems)) {
  
  ds_ecosystems_effect_size[[variable]] = ds_ecosystems %>%
    filter(
      
    # To have a cleaner dataset filter out time point 0, as ecosystems were assumed to be the same as the bottles from which they were started, as we only measured these bottles and not the ecosystems.
      
      time_point !=  0,
      
      # To have a cleaner dataset filter out ecosystems in which this variable could not be computed (e.g., species richness of a crashed culture). 
      
      !is.na(!!sym(variables_ecosystems[variable]))) %>%
    
    # To afterwards calculate effect sizes, get the mean, sd, and sample size of treatments at each time point 
    
    group_by(across(all_of(c("time_point",
                             "day",
                             "ecosystem_type",
                             "ecosystem_size_and_trophy",
                             "connection",
                             "ecosystem_size",
                             "ecosystem_size_ml",
                             "trophic_type",
                             "metaecosystem_type")))) %>%
    summarise(across(all_of(variables_ecosystems[variable]),
                     list(mean = mean,
                          sd = sd)),
              sample_size = n()) %>%
    
    # To know of which variable the sample size is when you afterwards bind columns, add the name of the variable to the name of the sample size column. 
    
    rename_with( ~ paste0(variables_ecosystems[variable], 
                          "_sample_size"),
                 matches("sample_size"))
}

# To have in the rows treatment and in the columns means, sd, and sample size, bind columns together. 

ds_ecosystems_effect_size <- reduce(ds_ecosystems_effect_size,
                                    full_join,
                                    by = c("time_point",
                                           "day",
                                           "ecosystem_type",
                                           "ecosystem_size_and_trophy",
                                           "connection",
                                           "ecosystem_size",
                                           "ecosystem_size_ml",
                                           "trophic_type",
                                           "metaecosystem_type"))
```

```{r echo=FALSE}
expect_equal(nrow(ds_ecosystems_effect_size),
             (n_controls + n_treatments) * (length(time_points) - 1))
```

```{r}

## - Calculate Hedge's d. - ##

# Initialise the effect size columns 

for (variable in length(variables_ecosystems)) {
  ds_ecosystems_effect_size <- ds_ecosystems_effect_size %>%
    mutate(!!paste0(variables_ecosystems[variable], "_d") := NA,
           !!paste0(variables_ecosystems[variable], "_d_upper") := NA,
           !!paste0(variables_ecosystems[variable], "_d_lower") := NA)
}
  
row_n = 0

# For each treatment at each time point, calculate effect size and 95% CI

for (treatment in 1:nrow(treatments_and_controls)) {
    
  for (time_p in 1:length(time_points_for_ES)) {
    
    row_n = row_n + 1
    
    treatment_row = ds_ecosystems_effect_size %>%
      filter(ecosystem_type == treatments_and_controls$treatment[treatment],
             time_point == time_points_for_ES[time_p])
      
    control_row = ds_ecosystems_effect_size %>%
      filter(ecosystem_type == treatments_and_controls$control[treatment],
             time_point == time_points_for_ES[time_p])
      
      for (variable in 1:length(variables_ecosystems)) {
        
        hedges_d = calculate.hedges_d(
          treatment_row[[paste0(variables_ecosystems[variable], "_mean")]],
          treatment_row[[paste0(variables_ecosystems[variable], "_sd")]],
          treatment_row[[paste0(variables_ecosystems[variable], "_sample_size")]],
          control_row[[paste0(variables_ecosystems[variable], "_mean")]],
          control_row[[paste0(variables_ecosystems[variable], "_sd")]],
          control_row[[paste0(variables_ecosystems[variable], "_sample_size")]])
        
        ds_ecosystems_effect_size[[paste0(variables_ecosystems[variable], "_d")]][
          ds_ecosystems_effect_size$ecosystem_type ==
           treatments_and_controls$treatment[treatment] &
          ds_ecosystems_effect_size$time_point == 
           time_points_for_ES[time_p]] =
          hedges_d$d
        
        ds_ecosystems_effect_size[[paste0(variables_ecosystems[variable], "_d_upper")]][
          ds_ecosystems_effect_size$ecosystem_type ==
           treatments_and_controls$treatment[treatment] &
          ds_ecosystems_effect_size$time_point == 
           time_points_for_ES[time_p]] =
          hedges_d$upper_CI
        
        ds_ecosystems_effect_size[[paste0(variables_ecosystems[variable], "_d_lower")]][
          ds_ecosystems_effect_size$ecosystem_type ==
           treatments_and_controls$treatment[treatment] &
          ds_ecosystems_effect_size$time_point == 
           time_points_for_ES[time_p]] =
          hedges_d$lower_CI
        
      }
    }
  }
```

```{r echo=FALSE}
expect_equal(nrow(ds_ecosystems_effect_size), 
             (n_treatments + n_controls) * (length(time_points) - 1))
```

```{r}

## - Retain only the connected ecosystems, discarding the controls (unconnected). - ##

ds_ecosystems_effect_size = ds_ecosystems_effect_size %>%
  filter(connection == "connected")
```

However, Hedge's d because of how much it depends on the pooled spread of the treatment and control might be harder to interpret than the log response ratio. Therefore, even though the log response ratio might not be calculated for all the protist species, we also decide to calculate it as well. To calculate the log response ratio of the dominance of protist species I use here the package `SingleCaseES` (see [this link](https://cran.r-project.org/web/packages/SingleCaseES/vignettes/Using-SingleCaseES.html)). This package. The package provides the function `LRRi` which calculates effect sizes for a single study case. It also adjust for small sample sizes by default.

```{r}

## - Calculate the effect size (Log Response Ratio). - ##

# Initialise the effect size columns 

for (variable in length(protist_species_dominance)) {
  ds_ecosystems_effect_size <- ds_ecosystems_effect_size %>%
    mutate(!!paste0(protist_species_dominance[variable], "_LRR") := NA,
           !!paste0(protist_species_dominance[variable], "_LRR_upper") := NA,
           !!paste0(protist_species_dominance[variable], "_LRR_lower") := NA)
}
  
row_n = 0

# For each treatment, time point, and variable calculate LRR and 95% CI

for (treatment in 1:nrow(treatments_and_controls)) {
    
  for (time_p in 1:length(time_points_for_ES)) {
    
      for (variable in 1:length(protist_species_dominance)) {
        
        row_n = row_n + 1
        
        treatment_values = ds_ecosystems %>%
          filter(ecosystem_type == treatments_and_controls$treatment[treatment],
                 time_point == time_points_for_ES[time_p],
                 !is.na(!!sym(protist_species_dominance[variable]))) %>%
          pull(!!sym(protist_species_dominance[variable]))
        
        control_values = ds_ecosystems %>%
          filter(ecosystem_type == treatments_and_controls$control[treatment],
                 time_point == time_points_for_ES[time_p],
                 !is.na(!!sym(protist_species_dominance[variable]))) %>%
          pull(!!sym(protist_species_dominance[variable]))
    
        # By default it corrects for small sample sizes and calculates 95 % CI.
        
        LRR_output = LRRi(A_data = control_values, 
                          B_data = treatment_values, 
                          scale = "proportion")
        
        ds_ecosystems_effect_size[[paste0(protist_species_dominance[variable], "_LRR")]][
          ds_ecosystems_effect_size$ecosystem_type ==
           treatments_and_controls$treatment[treatment] &
          ds_ecosystems_effect_size$time_point == 
           time_points_for_ES[time_p]] =
          LRR_output$Est
        
        ds_ecosystems_effect_size[[paste0(protist_species_dominance[variable], "_LRR_upper")]][
          ds_ecosystems_effect_size$ecosystem_type ==
           treatments_and_controls$treatment[treatment] &
          ds_ecosystems_effect_size$time_point == 
           time_points_for_ES[time_p]] =
          LRR_output$CI_upper
        
        ds_ecosystems_effect_size[[paste0(protist_species_dominance[variable], "_LRR_lower")]][
          ds_ecosystems_effect_size$ecosystem_type ==
           treatments_and_controls$treatment[treatment] &
          ds_ecosystems_effect_size$time_point == 
           time_points_for_ES[time_p]] =
          LRR_output$CI_lower
        
      }
    }
  }
```
