---
title: "Untitled"
output: html_document
date: "2024-10-21"
editor_options: 
  chunk_output_type: console
---

### Running time

```{r running-time, echo = FALSE, eval = TRUE}
end_time = Sys.time()
end_time - start_time
```

### Presentation plots meta-ecosystems

```{r child = here("2_r_files", "22_present_metaecos.Rmd")}
```

### Presentation plots AD ecosystems

Create plots for presentations on how ecosystem biomass changed across connected and unconnected types. Start from plotting an empty figures and then show one line at the time.

```{r}
metaecosystem_type_selected = "AD"
```

```{r child = here("2_r_files", "23_present_ecos.Rmd")}
```

### Presentation plots HD ecosystems

Create plots for presentations on how ecosystem evenness changed across connected and unconnected meta-ecosystem types. Start from plotting an empty figures and then show one line at the time.

```{r}
metaecosystem_type_selected = "HD"
```

```{r child = here("2_r_files", "23_present_ecos.Rmd")}
```

### Oven Test

```{r child = here("2_r_files", "26_test_OvenTest.Rmd")}
```

### EugGrowth Test

```{r child = here("2_r_files", "27_test_EugGrowth.Rmd")}
```

### Useful code

If you want to change a certain part of the code using the following code in Unix:

```{batch eval = FALSE}
#Rmd script
cd /Users/ema/Documents/GitHub/AHSize/r_files; sed -i '' 's/old_string/new_string/g' *.Rmd

#R script
cd /Users/ema/Documents/GitHub/AHSize/r_files/functions; sed -i '' 's/old_string/new_string/g' *.R
```

If you want to share a dataset and get a reproducible object, use the following R code:

```{batch eval = FALSE}
dput(data)
```

### Sampled rows

This are 20 random columns of ds_metaecosystems that you can use to input into chatGPT to give it an idea of what the structure of your data is.

```{r}
ds_metaecosystems %>% 
  sample_n(20, 
           replace = FALSE) %>%
  dput()
```

```{r echo=FALSE, message=FALSE}
#Save environment
save.image(file = here("3_results", "environments", "environment_at_the_of_knitting.RData"))
```

